---
title: "Coding Assignment 3"
author: "Team 11"
date: "Due: 2021-12-09 23:59"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
#Put any packages you need here
library(readxl)
library(dplyr) # for pipe operator
library(gt) # for fancier tables
library(gtsummary) # for fancier summary statistics
library(corrplot) # for fancier correlations
library(car) # for easier scatterplots
library(jtools) # for fancier regression output
library(plotly)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0026_Group11.csv")

```



## Question 1

Randomly select three observations from the sample and exclude from all modeling (i.e. n=47). Provide the summary statistics (min, max, std, mean, median) of the quantitative variables for the 47 observations.

```{r q1}
set.seed(123457)
insuranceremove3 <- insurance[-sample(1:nrow(insurance), 3), ]
removequalitative1 <- insuranceremove3[,c('Charges','Age','BMI','Children')]

sd(removequalitative1$Charges, na.rm = TRUE)
sd(removequalitative1$Age, na.rm = TRUE)
sd(removequalitative1$BMI, na.rm = TRUE)
sd(removequalitative1$Children, na.rm = TRUE)

index <- sample(seq_len(nrow(insuranceremove3)), size = 3)
train <- insuranceremove3[-index,]
test <- insuranceremove3[index,]



train %>% 
  tbl_summary(statistic = list(all_continuous() ~ c("{mean} ({sd})",
                                                    "{median} ({p25}, {p75})",
                                                    "{min}, {max}"),
                              all_categorical() ~ "{n} / {N} ({p}%)"),
              type = all_continuous() ~ "continuous2")

```
By randomly removing three observations from the model the data shown above was derived. The Standard Deviations for Charges, Age, BMI, and Children are as follows $10,123.25, 14.20385 years, 6.303552, 1.201679.

## Question 2

Provide the correlation between all quantitative variables

```{r}
cor(removequalitative1)

corrplot(cor(removequalitative1),
type = "lower",
order = "hclust",
tl.col = "black",
tl.srt = 45,
addCoef.col = "black",
diag = FALSE)



```
The quantitative variables are Charges, Age, BMI, Children. The correlation between all quantitative variables is shown above. Based on the data above, Age is positively correlated to Charges. As well as, BMI and Charges, Children and Charges. Insurance Premiums would increase based on an increase in age, BMI and to some small degree the number of children you have.

## Question 3

Run a regression that includes all independent variables in the data table. Does the model above violate any of the Gauss-Markov assumptions? If so, what are they and what is the solution for correcting?

```{r}
model <- lm(Charges~ Age + BMI + Female + Children + Smoker +WinterSprings + WinterPark + Oviedo, data = insuranceremove3)
summary(model)

par(mfrow=c(1,2))
hist(train$Charges) #before

train$lnCharges <- log(train$Charges)

hist(train$lnCharges) #after

hist(train$Age)
train$lnAge <- log(train$Age)

hist(train$lnAge)

hist(train$Children)
train$lnChildren <- log(train$Children)

hist(train$lnChildren)

hist(train$BMI)
train$lnBMI <- log(train$BMI)

hist(train$lnBMI)

scatterplotMatrix(train[,c(1,2,3,5)]) 
```
Charges is not normally distributed and Age is a bimodal distribution which violates the third Gauss-Markov assumption because it is not a linear relationship. By transforming the data with a log relationship this will fix the assumption violation.

## Question 4

Implement the solutions from question 3, such as data transformation, along with any other changes you wish. Use the sample data and run a new regression. How have the fit measures changed? How have the signs and significance of the coefficients changed?

```{r q3}
par(mfrow=c(2,2))
plot(train$Charges)

par(mfrow=c(2,2))
plot(train$Age)

model_1 <- lm(train$lnCharges ~., data = train[,c(2,3,5,10)] )

summary(model_1)

tbl_regression(model_1,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_1)$adj.r.squared* 100,digits = 2),"%")))

par(mfrow=c(2,2))
plot(model_1)

model_2 <- lm(train$lnAge ~., data = train[,c(2,3,5,11)] )

summary(model_2)

tbl_regression(model_2,
               estimate_fun =  ~style_sigfig(.x, digits = 4)) %>% as_gt() %>%
  gt::tab_source_note(gt::md(paste0("Adjusted R-Squared: ",round(summary(model_2)$adj.r.squared* 100,digits = 2),"%")))

par(mfrow=c(2,2))
plot(model_2)

```
When comparing the original model vs. model_2 the adjusted R-square increased from .76 to .97. Similarly, the P-value increased from 2.993e-11 to 2.2e-16. Therefore, there is a significant increase in the fit  of our model. 

## Question 5

Use the 3 withheld observations and calculate the performance measures for your best two models. Which is the better model? (remember that "better" depends on whether your outlook is short or long run)

```{r q4}

test$lnCharges <- log(test$Charges)
test$lnAge <- log(test$Age)
test$AgeSquared <- test$Age^2

test$model_1 <- predict(model_1, newdata = test)

test$model_2 <- predict(model_2,newdata = test) %>% exp()

test$errormodel_1 <- test$model_1 - test$Charges

test$errormodel_2 <- test$model_2 - test$Charges


mean(test$errormodel_1)

mean(test$errormodel_2)

mae <- function(error_vector){
  error_vector %>% 
  abs() %>% 
  mean()
}


mae(test$errormodel_1)

mae(test$errormodel_2)

rmse <- function(error_vector){
   error_vector^2 %>% 
  mean() %>% 
  sqrt()

}


rmse(test$errormodel_1)
rmse(test$errormodel_2)

mape <- function(error_vector, actual_vector){
  (error_vector/actual_vector) %>% 
    abs() %>% 
    mean()
}


mape(test$errormodel_1, test$Charges)

mape(test$errormodel_2, test$Age)

```

Based on our calculations, model_2 is the better performing model. Comparing the two models, Model_2 has a slightly lower mean, MAE, RMSE. However, the MAPE is significantly larger which does not support model_2.

## Question 6

Provide interpretations of the coefficients, do the signs make sense? Perform marginal change analysis (thing 2) on the independent variables.

```{r}

# The coefficients are significantly smaller in model_2, the sign in BMI is now negative but was not statistically significant in our model. 
```

## Question 7

An eager insurance representative comes back with five potential clients. Using the better of the two models selected above, provide the prediction intervals for the five potential clients using the information provided by the insurance rep.

| Customer | Age | BMI | Female | Children | Smoker | City           |
| -------- | --- | --- | ------ | -------- | ------ | -------------- | 
| 1        | 60  | 22  | 1      | 0        | 0      | Oviedo         |
| 2        | 40  | 30  | 0      | 1        | 0      | Sanford        |
| 3        | 25  | 25  | 0      | 0        | 1      | Winter Park    |
| 4        | 33  | 35  | 1      | 2        | 0      | Winter Springs |
| 5        | 45  | 27  | 1      | 3        | 0      | Oviedo         |

```{r}
potential1 <- data.frame(Age = 60,
                            BMI = 22,
                            Children = 0,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 1)
potential2 <- data.frame(Age = 40,
                            BMI = 30,
                            Children = 1,
                            Female = 0,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 1)
potential3 <- data.frame(Age = 25,
                            BMI = 25,
                            Children = 0,
                            Female = 0,
                            Smoker = 1,
                            WinterSprings = 0,
                            WinterPark = 1,
                            Oviedo = 0)
potential4 <- data.frame(Age = 33,
                            BMI = 35,
                            Children = 2,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 1,
                            WinterPark = 0,
                            Oviedo = 0)
potential5 <- data.frame(Age = 45,
                            BMI = 27,
                            Children = 3,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 1)

predict(model_2, newdata = potential1, interval = 'prediction')

predict(model_2, newdata = potential2, interval = 'prediction')

predict(model_2, newdata = potential3, interval = 'prediction')

predict(model_2, newdata = potential4, interval = 'prediction')

predict(model_2, newdata = potential5, interval = 'prediction')

```

## Question 8

The owner notices that some of the predictions are wider than others, explain why.

By looking at the prediction values used in the model the values are outside the normal mean used to test the model therefore, the values would be outside what we expect potentially causing a wider prediction interval.

If predictions vary very widely it could be due to issues with model specification bias or not including the qualitative data when devising a model therefore the values included when predicting the models will not be as efficient.

## Question 9 

Are there any prediction problems that occur with the five potential clients? If so, explain.

Prediction problems occur when the model doesn't take into consideration qualitative variables such as location or  when factors used in the predictions such as AGE, BMI are outside the normal variables used to develop the model.



