---
title: "Coding Assignment 2"
author: "Team 11"
date: "Due: 2021-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0026_Group11.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1}
model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)

summary(model)

```

Charges = -11700.62 + 272.66Age + 361.03BMI + 863.03Children -734.6Female + 24518.3Smoker +339.0 WinterSprings -3507.3WinterPark -857.5Oviedo

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$

At the alpha = .2 level 

These Test as Significant:
Age (p-value=2.52e-05), BMI (p-value=0.00605), Children (p-value=0.11833), Smoker (p-value=1.08e-12 ), and Winter Park (p-value= 0.06916) all have a p-value that is less than alpha=0.2 therefore we reject the null and these independent variables are significant. 


These do NOT test as significant
Female (p-value= 0.62870 ), Winter Springs (p-value=0.86291 ) and Oviedo (p-value=0.69141) all have a p- value that is greater than alpha=0.2 therefore we can not reject the null and these independent variables are not significant. 

## Question 2

Interpret the coefficients of all the independent variables that tested significant.

Based on our alpha = 0.2 these values tested significant and their respective margin of error with an 80% confidence interval for the impact on the insurance premiums are as described below. 

Age increase premiums 231.6 per year of age. The margin of error for this variable is +/- 1.3(48.8) or +/-63.44.

BMI increase premiums 332.5 per one point increase in BMI. The margin of error for this variable is +/- 1.3 (114.8) or +/- 149.24.

Children increase premiums 1010.3 per each additional dependent. The margin of error for this variable is+/- 1.3 (633.3) or +/- 823.29.

Winter Park decreases premiums -3507.3 based on location. The margin of error for this variable is +/- 1.3 (1879.2) or +/- 2255.04.



## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}
newPrediction <- data.frame(Age = 35,
                            BMI= 26,
                            Children =1,
                            Female= 1,
                            Smoker= 0,
                            WinterSprings= 0,
                            WinterPark= 0,
                            Oviedo= 0)

                
predict(model, newdata = newPrediction)

predict(model, 
        newdata = newPrediction, 
        interval = "confidence",
        level = .95)
```

Based on this data we are 95% confident that the new client applying for coverage would likely use $6377 in medical expenses plus or minus $3326.

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}
charges_reduced <- insurance[, -(7:9)] # drops last 3 columns

model_reduced <- lm(Charges ~. , data = charges_reduced)

summary(model_reduced)

model2 <- lm(Charges ~ Age + BMI + Children + Female + Smoker, data = insurance)

summary(model2)

regsummary <- summary(model)

regsummary$fstatistic 

anova(model2, model)

```

The F-statistic for the partial is 30.95 on 5 explanatory variables and has 44 Degrees of Freedom. The model that contains all the variables has an F-statistic of 20.6 on all 8 explanatory variables and 41 Degrees of Freedom. In this instances the partial F is greater than the original models F statistic which means that the group of variables in the partial F-test are significant. 
